Bayesian Data Analysis, Rough Draft

### 2023-12-01 Lahman Analysis/Formal Analysis/Draft1.qmd
Added notes for future self

>>>>

In explore results, discuss both the trajectories of about 4-5 players and show how they change (probably want to sample about 10 just to be safe). But then, just for fun, look at which player has the highest $\alpha$ level since that would be my models prediction of best HR hitter independent of everything else. It will probably be Barry Bonds.
